### 2013-01-25 patchy-selection-paper.tex
/* Patchy Selection paper */

Combining this with the calculations above allows us to get a rough sense of the scale of migration between separated patches,
supposing that patches are large enough for local fixation to be stable. If the alleles were not advantageous in the second patch,
the average number of mutant alleles present in a small area $\Delta$
near the second patch, due
to migration from the first patch, would be $\approx \rho A \exp( -
|\sqrt{s_m} R/\sigma| ) \Delta$. Assuming that the patch is
sufficiently large to give an allele a $2s_B$ probability of becoming established, the rate at which migrants find
themselves in the patch and become established  is approximately
\begin{equation}
\lamda_{Mig,R} = \rho A^2 s_B \exp( -|\sqrt{s_m} R/\sigma| ).
\end{equation}
\gc{Is this $A^2$ right here?. Do we want to use $q(R)$ here?}
If this establishment rate is low, the time it takes
a mutation to arise that will become established will be  $\sim Exp(\lambda_{mig,R})$
Assuming that the time it takes for a allele from the first patch to
become established in the second patch is short,
then  the expected waiting time until some migrant allele fixes in the
second patch will be $T_{Mig} = 1/\lamda_{Mig,R} $.

@@

Taking the expressions from sections \ref{ss:patchymutation} and \ref{ss:patchymigration} above,
we see that if patches each have sufficiently large area $A$,
then the mutational input in each is on the order of $2 s_B \rho \mu A$,
while the influx due to migration between patches separated by
distance $R$ is on the order $2 s_B \rho A \exp(- |\sqrt{s_m}
R/\sigma|)$ \gc{check $A^2$}. 
If the input from mutation and migration are comparable, i.e.\ if $\mu \approx \exp( -|\sqrt{s_m} R/\sigma| )$,
then adaptation is expected to take place both by migration and
mutation.

@@

If we are willing to take these approximations at face
value, and assuming both rates are small, the probability of parallel
adaptation is 
\begin{equation}
\frac{\mu}{\mu + \exp(- |\sqrt{s_m} R/\sigma|}
\end{equation}
so that the probability of parallel mutation should increase
approximately logistically with the distance between the patches at a
rate $\sqrt{s_m} /\sigma$. However, we caution that these calculations
are rough and so should be taken wi

>>>>

\gc{work in a parameter that the the migrant outflux of a patch, and
  explain that depends on geometry }

Combining this with the calculations above allows us to get a rough sense of the scale of migration between separated patches,
supposing that patches are large enough for local fixation to be stable. If the alleles were not advantageous in the second patch,
the average number of mutant alleles present in a small area $\Delta$
near the second patch, due
to migration from the first patch, would be $\approx \rho E \exp( -
|\sqrt{s_m} R/\sigma| ) \Delta$. Assuming that the patch is
sufficiently large to give an allele a $2s_B$ probability of becoming established, the rate at which migrants find
themselves in the patch and become established  is approximately
\begin{equation}
\lambda_{Mig,R} = \rho E s_B \exp( -|\sqrt{s_m} R/\sigma| ).
\end{equation}
\gc{Is this $A^2$ right here?. Do we want to use $q(R)$ here?}
If this establishment rate is low, the time it takes
a mutation to arise that will become established will be  $\sim Exp(\lambda_{mig,R})$
Assuming that the time it takes for a allele from the first patch to
become established in the second patch is short,
then  the expected waiting time until some migrant allele fixes in the
second patch will be $T_{Mig} = 1/\lamda_{Mig,R} $.

@@

Taking the expressions from sections \ref{ss:patchymutation} and \ref{ss:patchymigration} above,
we see that if patches each have sufficiently large area $A$,
then the mutational input in each is on the order of $2 s_B \rho \mu A$,
while the influx due to migration between patches separated by
distance $R$ is on the order $2 s_B \rho E \exp(- |\sqrt{s_m}
R/\sigma|)$. \gc{what to assume about A and $E$ here?}
If the input from mutation and migration are comparable, i.e.\ if $\mu \approx \exp( -|\sqrt{s_m} R/\sigma| )$,
then adaptation is expected to take place both by migration and
mutation.

@@

If we are willing to take these approximations at face
value, and assuming both rates are small, the the time till the first
patch is colonized will be approximately exponentially
distributed with parameter $2 \lambda_{Mut}$. Then time till the
second patch is subsequently colonized by the $B$
allele (via either migration or new mutation) will be exponentially
distributed with parameter $\lambda_{Mut}+\lambda_{Mig,R}$. Both of
these times scale linearly with $1/(\rho s_{B})$, so that

then probability of parallel
adaptation is 
\begin{equation}
\frac{\lambda_{Mut}}{\lambda_{Mut} + \lambda_{Mig,R}} = \frac{\mu (A/E)}{\mu (A/E) + \exp(- |\sqrt{s_m} R/\sigma|}
\end{equation}
so that the probability of parallel mutation should increase
approximately logistically with the distance between the patches at a
rate $\sqrt{s_m} /\sigma$. However, we caution that these calculations
are rough and so should be treated mainly as a rule of thumb.

We can extend this reasoning to multiple patches ($>2$) within our population's range
where our $B$ allele can facilitate local adaptation. Under our
assumptions of mutational exclusion and rapid establishment, each one
of these patches will adapt through a single copy of the $B$
alllele. The occupation of our different patches by the $B$ allele will form a
discrete state markov chain, where the states of the chain are which patches have
been colonized so far by $B$, and which colonized patches have shared
versus distinct copy of $B$.

For simplicity we will assume that each of these patches has
the same size and geometry (i.e. same $E$). A particular patch adapts in parallel through an independent
instance of the $B$ mutation at rate $2 s_B \mu \rho A$.
While, if patches $1$ through $k$ are already occupied by
established copies of the $B$ allele, and these patches are at
distances $R_1,~\cdots,~R_k$ away from our patch, the rate of
adaptation through migration in our patch is 
\begin{equation}
\sum_{i=1}^{k} 2 s_B \rho E \exp(- |\sqrt{s_m} R_k/\sigma|}.
\end{equation}
Once again the compound parameter $2s_B \rho$ will function to
scale the times between events (parallel adaptation or the spread of a
migrant), and so is critical to the time-scale over which
adaptation occurs. However, this compound parameter again has no effect on
the final configuration of the pattern of which patches have adapted
in parallel versus have shared genetic basis to their adaptive
response to the poor environment.

The states of this
